The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach

### 2023-01-25 analysis/paper/paper.qmd

# clean text 
emu_theses$text_clean <- emu_theses$text %>%
  str_replace_all("\\s", " ") %>%  ### remove all carriage return and newline characters
  # str_replace_all("- ", "") %>%       ### remove all hyphens
  # str_replace_all("[0-9]", "") %>%    ### remove all numbers
  str_replace_all(emu_theses$first_name, "") %>%   ### remove author first name
  str_replace_all(emu_theses$last_name, "") %>%     ### remove author surname
  str_replace_all(emu_theses$title, "") %>%              ### remove title
  str_replace_all("EMU", "") %>%           ### remove common words
  str_squish()
```

>>>>

#head_text(emu_theses$text)

# clean text 
emu_theses$text_clean <- emu_theses$text %>%
  clean_basic() %>%
  str_remove_all(find_meta_stopwords(emu_theses) )

```
